Walling up Backdoors in Intrusion Detection Systems

### 2019-10-15 paper/paper.tex
Add GENESIDS reference and fix some other things

% Modify this to remove all ACM and conference information (for arXiv for example)
\def\removeHeaders{yes}

\def\tempYes{yes}
\documentclass[10pt,sigconf,letterpaper,dvipsnames\ifx\removeHeaders\tempYes ,nonacm\fi]{acmart}
\acmYear{2019}
\copyrightyear{2019}
\acmConference{CoNEXT '19}{December 9-12, 2019}{Orlando, Florida, USA}

@@

@@

\paragraph{\gls{ml} Techniques}
%\subsubsection{Deep Learning}
We used PyTorch~\cite{paszke_automatic_nodate} to build an \gls{mlp}.
% neural network classifier.
For this we used 5 fully connected layers with 512 neurons each. We applied \gls{relu} activation after each layer and dropout with a probability of 0.2 and used binary cross entropy  as loss function for training. % for the classification task itself.

%\subsubsection{\glspl{rf}}
In addition to the \gls{mlp}, we trained an \gls{rf} classifier to detect attacks in network traffic. We used the RandomForestClassifier implementation from scikit-learn~\cite{pedregosa_scikit-learn_2011} for this task and used 100 estimators for training the \gls{rf}.

@@

\begin{figure*}[h]
\includegraphics[width=\textwidth]{pruning_example.pdf}
\caption{Example of a \gls{dt} being pruned.}
\label{fig:pruningExample}
\end{figure*}

@@

Our experiments revealed that pruning does not remove the backdoor at all, while decreasing the accuracy for normal data if too many neurons are pruned. To check whether other reasons are responsible for the \gls{mlp}'s failure to remove the backdoor, we also conducted the following experiments: \begin{enumerate*} \item We did not take the average activation but the average of the binary activations of each neuron, which means that we did not consider the quantity of the activation but only if the activation is larger than 0 and then averaged the activations for all data samples. \item We checked whether the dropout regularization might be the reason. \item We hypothesized that the issue might be that there are a lot fewer malicious samples in the dataset than there are attacks. Thus we reversed the backdoor and made the backdoor so that it would falsely classify benign samples as malicious ones.
\end{enumerate*}

@@

\autoref{fig:pruningExample} shows an example of variant (3) of pruning applied to a tree
\begin{figure}[h]
\includegraphics[width=\columnwidth]{figures/prune_CAIA_backdoor_15/prune_oh_d.pdf}
\caption{Pruning an \gls{rf} for \unsw{}.}
\label{fig:performancePruningRF}
\end{figure}
%\todo{Max: Which pruning algorithm actually?}
and \autoref{fig:performancePruningRF} shows the resulting accuracy for pruning according to variant (3) for the \unsw{} dataset. With sufficient leaves being pruned, the accuracy of the backdoor approaches zero. The accuracy for the regular data does not decrease, it might even increase by
%thanks to the the pruning also
reducing overfitting. %With a significantly smaller validation set, pruning takes longer to remove the backdoor
%until it works
%but it still works. This is an important finding as a large validation dataset makes it hard for users without access to expensive hardware to perform the pruning.
Even with a very small validation set of just 1\% of its original size, the pruning still works as expected.

@@

%We found it
It is surprising that the neural network pruning and fine-tuning methods were ineffective for removing the backdoor from our \gls{dl} model in all our experiments. This leads us to the conclusion that probably the proposed methods are insufficient for \glspl{mlp} and more research is required to develop methods suitable for them.

>>>>

% Modify this to remove all ACM and conference information (for arXiv for example)
\def\removeHeaders{no}

\def\tempYes{yes}
\documentclass[9pt,sigconf,letterpaper,dvipsnames\ifx\removeHeaders\tempYes ,nonacm\fi]{acmart}
\acmYear{2019}
\copyrightyear{2019}
\acmConference{CoNEXT '19}{December 9-12, 2019}{Orlando, Florida, USA}

@@

While we aim at sanitizing possibly backdoored \glspl{ids}, \cite{erlacher_how_2018} take a different approach: They create \textit{GENESIDS}, a tool that enables extensive testing of an \gls{ids}. This approach can potentially also uncover backdoors if it finds a case, in which the \gls{ids} surprisingly misbehaves.

@@

\paragraph{\gls{ml} Techniques}
%\subsubsection{Deep Learning}
We used PyTorch~\cite{paszke_automatic_2017} to build an \gls{mlp}.
% neural network classifier.
For this we used 5 fully connected layers with 512 neurons each. We applied \gls{relu} activation after each layer and dropout with a probability of 0.2 and used binary cross entropy  as loss function for training. % for the classification task itself.

%\subsubsection{\glspl{rf}}
In addition to the \gls{mlp}, we trained an \gls{rf} classifier to detect attacks in network traffic. We used the RandomForestClassifier implementation from scikit-learn~\cite{pedregosa_scikit-learn:_2011} for this task and used 100 estimators for training the \gls{rf}.

@@

\begin{figure*}[h]
\includegraphics[width=\textwidth]{pruning_example.pdf}
\caption{Toy example of a \gls{dt} being pruned. The decision trees of the random forests we use usually have many thousands of leaves and decisions and are thus not trivial to visualize.}
\label{fig:pruningExample}
\end{figure*}

@@

Our experiments revealed that pruning does not remove the backdoor at all, while decreasing the accuracy for normal data if too many neurons are pruned. To check whether other reasons are responsible for the \gls{mlp}'s failure to remove the backdoor, we also conducted the following experiments: \begin{enumerate*} \item We did not take the average activation but the average of the binary activations of each neuron, which means that we did not consider the quantity of the activation but only if the activation is larger than 0 and then averaged the activations for all data samples. \item We checked whether the dropout regularization might be the reason. \item We hypothesized that the issue might be that there are a lot fewer malicious samples in the dataset than benign ones. Thus we reversed the backdoor and made the backdoor so that it would falsely classify benign samples as malicious ones.
\end{enumerate*}

@@

\autoref{fig:pruningExample} shows an example of variant (3) of pruning applied to a tree
\begin{figure}[h]
\includegraphics[width=\columnwidth]{figures/prune_CAIA_backdoor_15/prune_oh_d.pdf}
\caption{Pruning an \gls{rf} for \unsw{}.}
\label{fig:performancePruningRF}
\end{figure}
%\todo{Max: Which pruning algorithm actually?}
and \autoref{fig:performancePruningRF} shows the resulting accuracy for pruning according to variant (3) for the \unsw{} dataset. With sufficient leaves being pruned, the accuracy of the backdoor approaches zero. The accuracy for the regular data does not decrease significantly. It might even increase by reducing overfitting. With 90\% of leaves pruned, accuracy is still well above 99\%. Even with a very small validation set of just 1\% of its original size, the pruning still works as expected.

@@

%We found it
It is surprising that the neural network pruning and fine-tuning methods were ineffective for removing the backdoor from our \gls{dl} model in all our experiments. Since \glspl{cnn} are conceptually very similar to \glspl{mlp} it is not obvious that methods working for the former do not work for the latter. The difference that a \gls{cnn} always only looks at a portion of the input \cite{wikipedia_convolutional_2019} and not all of it (unlike an \gls{mlp}) should not change the efficacy of the pruning approach. This leads us to the conclusion that probably the proposed methods are insufficient for \glspl{mlp} and more research is required to develop methods suitable for them.
